Project Review Template

### 2023-04-28 Review_Troha_Aidan.qmd
Project Review

---
title: Project Review  
author: Kelly Hatfield
date: "`r file.mtime(knitr::current_input())`"
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

@@

Title of project:  COVID-19 Vaccination in Albany, GA

@@

Name of project reviewer: Kelly Hatfield

### Feedback and Comments
 The background and introduction are  thorough and proide good motiviation to the importance of the study.

The abstract could use help with clarity, perhaps reframe the study some: 
The outcome of interest is the change in the proportion of residents vacccinated over time from September - February. The predictor of interest is the COVID-19 vaccine hesitancy program intervention. It would be helpful also to help contextualize the three zip codes of interest.

@@

The hypotheis and questions can be more explicitly stated in the manuscript. For example, in the objectives section you mention data cleaning methods. The objective should be stated more succintly and explicitly:

We aim to assess any trend in vaccine uptake among our targeted community during the time of health literacy programs (September - February 2022)

Your hypothesis is a little unclear to me too. For example, you are looking for an increase in the number of Albany citizens who receive the vaccine in the time period. However, this is a value that can't decrease. So are you looking for an increase in the trend (interrupted tiem series), and increase in the daily rate among unvaccinated (where your denominator will change daily), an increase in the zip codes of interest versus other zip codes where targeted interventions werent applied? The objective/hypothesis might need to be fleshed out a bit more.

@@

The data structure is well explained and sources described. It is meddled in the with the importation and cleaning. I would rather encourage the author to separate the findings a bit.

@@

Data cleaning process is well described. Similar to comment above, it is interwoven with description of the data sources. The manuscript would benefit from separate paragraphs discussing these elements and some editorial review (e.g., ensuring run-on sentences are shortened, fragments removed). Some mentions of "data were cleaned" without explaining exaclty how. An example would be:

"For this analysis, we decided to exclude purina body condition scores as it was implemented later in the study, and most dogs do not have that information. The remaining columns were cleaned to make the data more consistent and in the format required for statistical analysis. "

could be streamlined to: 
"We excluded condition scores because they were not consistently collected and had high numbers of missing values. We recoded XXXX variables from XXX to XXX to facilitate easier statistical analysis.""

### Summary assessment

* some weaknesses in wrangling and exploratory component

@@

### Summary assessment
* defensible but not optimal analysis

@@

### Summary assessment
* results are presented ok, with room for improvement

@@

### Feedback and Comments
Discussion not present at time of review.

### Summary assessment

* strong, complete and clear discussion

@@

@@

### Summary assessment

* well structured

@@

### Summary assessment

* fully and well documented

@@

### Summary assessment

* fully reproducible without issues

@@

### Summary assessment

* strong level of thorougness

## Further comments
---

>>>>

---
title: Project Review Template 
author: AIDAN TROHA
date: "`r file.mtime(knitr::current_input())`"
format: 
  html:
    toc: true
    toc-depth: 3
    number-sections: true
---

@@

Title of project:

@@

Name of project reviewer: Aidan Troha

## Background, Context and Motivation
How well is the context of the project described? Is a comprehensive background, including summary of previous/related work given? Is the project well placed into the context of existing work (including proper referencing of existing work). Is it clear why the project was undertaken and what new information it hopes to provide?

I like the scope of your project here. I am interested to know if dealing with a smaller geographic location made finding data to use harder or easier to obtain.

@@

As with the introduction, the scope of your questioning is clearly defined. Are there any other covariates you looked into that you did not address in this section?

@@

Adding a link to info about the data source is a great way of providing necessary info without taking away from your analyses. I like this!

@@

The analyses employed make rational sense, and the steps seem easy enough to follow. I counldn't wrap my head around the structure of the README.md files, but that is just a style preference from me.

### Summary assessment
* some weaknesses in wrangling and exploratory component

@@

From what I can tell, the analyses are done appropriately and correctly. Good implementation of machine learning methods.

### Summary assessment
* strong and reasonable analysis

@@

There are plenty of figures to comment on. As a semantic argument, I wonder if you could find a way to collapse some of these figures into a more concise, paneled figure.

### Summary assessment
* results are very well presented

@@

As of review: no discussion or conclusion statements.

### Summary assessment
* major parts of discussion missing or wrong

@@

Great work so far!

@@

As the default structure, this is sufficient. Personally, I like a more intuitive structure wherein the steps of the analyses follow the order of the manuscript.

### Summary assessment
* mostly clear, but some confusing parts (e.g. useless files, things in the wrong folders)

@@

As per the previous response, it makes it difficult to track down where each file is located.

### Summary assessment
* decently documented with some gaps

@@

In the same vein as the previous, it can be difficult to fix an issue if you can't find the right file. In that, I mean it helps to have clearer readme files and intuitive file structure.

### Summary assessment
* small parts not reproducible or required manual intervention

@@

It is clear that you have put a lot of thought into this project as at each step your methods well argued and appropriate.

### Summary assessment
* strong level of thorougness

Great job! I can tell that you have put a lot of work into this project!
